\subsection{Client Class Definition:}
\textbf{Client Class:}  Is the root class in the client which responsible for establishing connection with the server.

\textbf{Methods definition:}
\textbf{ConnectToServer():}  Used to establish http connection with the server.



\subsection{Server Class Definition:}

\textbf{Server Class:}  Count connected clients to the server.Also contains Database Class and Agent Class which has a composition relation with the server. 

\textbf{Methods definition:}
\textbf{ListenToConnection():}  used to get the requested connection from client.

\subsection{Database Class Definition:}
\textbf{Database Class:}The database class, is the class responsible for connect the server to the database.Also Database Class contains two sub-classes which is ChatDatabase and UserDatabase.

\textbf{Methods definition:}
\textbf{ConnectToDatabase():} Used to connect to the database.

\subsection{ChatDatabase Class Definition:}
\textbf{Database Class:} Use connection created to take message sent from user to database to store it and show it to the user again while chatting.

\textbf{Methods definition:}
\textbf{reciveMessageFromUser():} Used to get message from the user .
\textbf{saveNewMessageToDatabase():} Used to save new  message from the user to database.
\textbf{retriveMessageFromDatabase():} Used to get message from the database .
\textbf{sendMessageToUser():} Used to send message saved on database to the user .

\subsection{UsersDatabase Class Definition:}
\textbf{UsersDatabase Class:} Used to identify that information entered are correct(user credentials)

\textbf{Methods definition:}
\textbf{receiveRequest():} Used to receive connection request from user.
\textbf{sign-in():} Used to sign in to the app using information has entered before by user .
\textbf{sign-out():} Used to sign out from the app.
\textbf{register():} Used to register a new account to the app by Fill all text fields showed to user.
\textbf{deleteAccount():} Used to delete account that user created.
\textbf{editAccount():} Used to edit account details or data that entered when user register.
\textbf{retriveAccountData():} Used to show user data.


--------------------------------------------------------------------------------
\section{Relevium Watchful Smart Helper}

\subsection{Description and priority}
Communicate with the application through phone's built-in assistant.
\subsection{Methodology}
We create intents in the agent that map user input to responses. In each intent, we define examples of user requests that can trigger the intent, what to extract from the request, and how to respond. Generally, an intent represents one dialog turn within the conversation. The agent would match that input to its corresponding intent and return the response you defined within that intent. The agent’s response usually prompts users for another utterance, which your agent will attempt to match another intent, and the conversation continues.
\subsection{Usability}
Relevium project uses  Watchful Smart Helper as a basic way to communicate with user. When the user log-in he/she will receive a welcome intent from pre-populated text responses from the responses Which has already been trained.

\section{Paramedic User}
\subsection{Description and priority}
One of the most important features During the disaster. When the user register to our application he/she will be asked to fill a form to prove that he/she a paramedic or not (optional),and if he/she fill this field, then he/she required to prove that by a picture for Work identity or any document Prove that he/she have the right to work with a paramedic degree.
\subsection{Guidelines}
There may be conditions under which the paramedic user will decide to get away or to be there to help others,there are no conditions for user to follow,he has full freedom to choose what he wants to do by helping others or escape in case of danger.

  


\begin{enumerate}
    \item
    \item

\end{enumerate}








